Multi sky-view\\ 3D aerosol distribution recovery

### 2013-10-04 article.tex
bookmark

\noindent{\bf Density of viewpoints}: Keeping the domain and scene ({\em Haze blobs}) fixed, we
repeated the reconstruction many times, each using a different subset of the above mentioned 36 simulated cameras. Each test randomly selected viewpoints, for various fixed values
of $N_{\rm views}< 36$. All rendered images used MC.
\Cref{fig:error_vs_cameras} plots the performance.
\begin{figure}[t]
  \centering
  \yoavcomment{\includegraphics{images/error_vs_cameras.pdf}}
  \caption{\small The relative error $\epsilon$ measure decreases with the number of
    cameras. Bars represent the standard deviation of $\epsilon$, over our random tests.}
  \label{fig:error_vs_cameras}
\end{figure}
Diminishing returns are obtained beyond $N_{\rm views}\approx 20$, which corresponds to $\approx 11$km separation between neighboring viewpoints. These tests point to fundamental questions about spatial-angular sampling: how spatially dense should cameras be, and how dense should a camera's field of view be sampled (in pixels)? This likely depends on the finesse of atmospheric structure sought, and the level of optical diffusion achieved by various aerosols. The novel tomography domain introduced here thus raises new important questions that will   require extensive further research.\\

\noindent{\bf Aerosol characteristics}: We used the {\em Haze blobs} scene, but varied the
aerosol characteristics. Compared to the aerosol described in \cref{sec:simul}, we tested two variations. In one variation, the phase function was isotropic, i.e.,
$[g_{\rm R},g_{\rm G},g_{\rm B}]=[0,0,0]$. In the other variation, the aerosol is partly absorbing: its single scattering albedo per color channel is
$[\varpi^{\rm aerosol}_{\rm R},\varpi^{\rm aerosol}_{\rm G},\varpi^{\rm aerosol}_{\rm B}]=
[0.69,0.74,0.78]$.  All rendered images used MC (See Figs.~\ref{fig:simulation_particles}(a)--(c)).
\begin{figure}[b]
  \centering
  \yoavcomment{\includegraphics{images/simulation_particles.pdf}}
  \caption{\small Images simulated by MC, from the same viewpoint, but different
  aerosol characteristics. (a) Haze blobs, characterized in Sec.~\ref{sec:simul}. 
  (b) Partly absorbing aerosol. (c) Aerosol having an isotropic phase function. (d) High aerosol density.}
  \label{fig:simulation_particles}
\end{figure}
Recovery results using $N_{\rm views}=36$ are shown in Figs.~\ref{fig:reconstructions}(a,b)
\begin{figure}[b]
  \centering
  \yoavcomment{\includegraphics{images/reconstructions.pdf}}
  \caption{\small  Recovered distributions when the aerosol is either party absorbing (a),
    has isotropic phase function (b) or has high density (c).}
  \label{fig:reconstructions}
\end{figure}
and in Table~\ref{tbl:mass}. The results indicate that if the aerosol's phase function has smaller anisotropy, recovery of the aerosol's density is easier. We hypothesise that tomography is better served by scattering isotropy, since then significant radiance from any voxel reach cameras in a wide range of directions. This may make back-projection (recovery from cameras to voxels) more accurate. On the other hand, if the phase function is strongly peaked around one direction, most cameras would not receive much radiance.

 that have mo\\

@@

We describe a way to sense the 3D atmosphere. It can help remote
sensing depart from common 1D aerosol distribution models, in favor
of detailed 3D RT analysis.  The paper describes both a novel data
acquisition system concept for this recovery task (ground-based camera
network), and a dedicated algorithm for reconstructing aerosol
distributions. Using more prior knowledge on the nature of
distributions will improve the recovery.

The estimation algorithm
uses a single scattering model. This approximation is valid when the
optical depth is small. However, as MC simulations show, it is
important to generalize the recovery algorithm so that high-order scattering
is included in it. Such generalization would be computationally complex:
in our tests, the MC forward model was slower by 2-3 orders of magnitude
than a single-scattering analytic model. Thus, inverting a 3D multiple-scattering
model requires research into numerical schemes for increasing the solution
efficiency of both forward and inverse problems.
The remote sensing community has devised several approaches to better approximate
multiple-scattering problems, mainly in one-dimensional models (e.g., successive
orders of scattering and discrete ordinates methods). We may tap into some of these approaches.
Deploying an experimental system will be needed: camera specifications~\cite{Pust2011}
should be set to optimally recover a wide range of aerosol distributions.
%\hl{The relation between the quantity and spatial distribution of
%  cameras and the quality of reconstruction should also be determined.}
%\fix{This requires}{These open questions require} a major theoretic
% and numerical research.

>>>>

\noindent{\bf Density of viewpoints}: Keeping the domain and scene ({\em Haze blobs}) fixed, we
repeated the reconstruction many times, each using a different subset of the above mentioned 36 simulated cameras. Each test randomly selected viewpoints, for various fixed values
of $N_{\rm views}< 36$. All rendered images used MC.
\Cref{fig:error_vs_cameras} plots the performance.
\begin{figure}[t]
  \centering
  \yoavcomment{\includegraphics{images/error_vs_cameras.pdf}}
  \caption{\small The relative error $\epsilon$ measure decreases with the number of
    cameras. Bars represent the standard deviation of $\epsilon$, over our random tests.}
  \label{fig:error_vs_cameras}
\end{figure}
Diminishing returns are obtained beyond $N_{\rm views}\approx 20$, which corresponds to $\approx 11$km separation between neighboring viewpoints. These tests point to fundamental questions about spatial-angular sampling: how spatially dense should cameras be, and how dense should a camera's field of view be sampled (in pixels)? This likely depends on the finesse of atmospheric structure sought, and the level of optical diffusion achieved by various aerosols. The novel tomography domain introduced here thus raises new theoretical questions that will   require extensive further research.\\

\noindent{\bf Aerosol characteristics}: We used the {\em Haze blobs} scene, but varied the
aerosol characteristics. Compared to the aerosol described in \cref{sec:simul}, we tested two variations. In one variation, the phase function was isotropic, i.e.,
$[g_{\rm R},g_{\rm G},g_{\rm B}]=[0,0,0]$. In the other variation, the aerosol is partly absorbing: its single scattering albedo per color channel is
$[\varpi^{\rm aerosol}_{\rm R},\varpi^{\rm aerosol}_{\rm G},\varpi^{\rm aerosol}_{\rm B}]=
[0.69,0.74,0.78]$.  All rendered images used MC (See Figs.~\ref{fig:simulation_particles}(a)--(c)).
\begin{figure}[b]
  \centering
  \yoavcomment{\includegraphics{images/simulation_particles.pdf}}
  \caption{\small Images simulated by MC, from the same viewpoint, but different
  aerosol characteristics. (a) Haze blobs, characterized in Sec.~\ref{sec:simul}. 
  (b) Partly absorbing aerosol. (c) Aerosol having an isotropic phase function. (d) High aerosol density.}
  \label{fig:simulation_particles}
\end{figure}
Recovery results using $N_{\rm views}=36$ are shown in Figs.~\ref{fig:reconstructions}(a,b)
\begin{figure}[b]
  \centering
  \yoavcomment{\includegraphics{images/reconstructions.pdf}}
  \caption{\small  Recovered distributions when the aerosol is either party absorbing (a),
    has isotropic phase function (b) or has high density (c).}
  \label{fig:reconstructions}
\end{figure}
and in Table~\ref{tbl:mass}. The results indicate that if the aerosol's phase function has smaller anisotropy, recovery of the aerosol's density is easier. We hypothesise that tomography is better served by scattering isotropy, since then significant radiance from any voxel reach cameras in a wide range of directions. This may make back-projection (recovery from cameras to voxels) more accurate. On the other hand, if the phase function is too strongly peaked around one direction, most cameras would not receive much scattered radiance from a voxel, undermining tomography. A very broad research is needed to verify and quantify such dependencies.\\

@@

We describe a way to sense the 3D atmosphere. It can help remote
sensing depart from common one-dimensional aerosol distribution models, in favor
of detailed 3D RT analysis.  The paper describes both a novel data
acquisition system concept for this recovery task (ground-based camera
network), and a dedicated algorithm for reconstructing aerosol
distributions. Using more prior knowledge on the nature of
distributions will improve the recovery.

The estimation algorithm
uses a single scattering model. This approximation is valid when the
optical depth is small. However, as MC simulations show, it is
important to generalize the recovery algorithm so that high-order scattering
is included in it. Such generalization would be computationally complex:
in our tests, the MC forward model was slower by 2-3 orders of magnitude
than a single-scattering analytic model. Thus, inverting a 3D multiple-scattering
model requires research into numerical schemes for increasing the solution
efficiency of both forward and inverse problems.
The remote sensing community has devised several approaches to better approximate
multiple-scattering problems, mainly in one-dimensional models (e.g., successive
orders of scattering and the discrete ordinates method). We may tap into some of these approaches.
Deploying an experimental system will be needed: camera specifications~\cite{Pust2011}
should be set to optimally recover a wide range of aerosol distributions.
%\hl{The relation between the quantity and spatial distribution of
%  cameras and the quality of reconstruction should also be determined.}
%\fix{This requires}{These open questions require} a major theoretic
% and numerical research.
